### 2015-08-04 usecase-ares.tex
a few small tweaks

ARES comprises 47 packages, with complex dependency relationships. 
Figure~\ref{fig:ares} shows the DAG for the current production configuration 
of ARES. At the top is ARES itself.  ARES depends on 11 LLNL physics packages,
4 LLNL math/meshing libraries, and 8 LLNL utility libraries.
The utility libraries handle tasks including logging, I/O, and 
performance measurement. ARES also uses 23 external software packages, 
including MPI, BLAS, Python, and many other libraries.  Together, these 
packages are written in a diverse set of languages including C, C++, 
Fortran, Python and tcl and uses MPI and OpenMP for parallelism.

@@

Altogether, the initial packaging effort required roughly two months 
for an experienced build engineer working 20 hours per week.
As shown in the table, 36 different configurations have been run using Spack
(some of 4 versions on each of 10 architecture-compiler-MPI combinations).
Prior to using Spack, only Linux/Intel configurations were automated. The ARES 
team listed a number of key features that enabled the increased automation:
\begin{enumerate}
\item Spack's version tracking and optional dependencies were required to
      build the four configurations with correct libraries;
\item The spec syntax allowed build scripts to concisely test compiler,
      compiler version, and dependency versions---a necessity
      for handling the different architectures;
\item Patching packages for particular platforms was
      necessary to build many packages; and
\item Using a DSL embedded in Python was a significant benefit;
      certain packages required custom scripting to patch.
\end{enumerate}

>>>>

ARES comprises 47 packages, with complex dependency relationships. 
Figure~\ref{fig:ares} shows the DAG for the current production configuration 
of ARES. At the top is ARES itself.  ARES depends on 11 LLNL physics packages,
4 LLNL math/meshing libraries, and 8 LLNL utility libraries.
The utility libraries handle tasks including logging, I/O, and 
performance measurement. ARES also uses 23 external software packages, 
including MPI, BLAS, Python, and many other libraries.  Together, these 
packages are written in a diverse set of languages including C, C++, 
Fortran, Python and tcl.
%% Sense of the following has been lost and seems unnecessary
%% and uses MPI and OpenMP for parallelism.

@@

Altogether, the initial packaging effort required roughly two months 
for an experienced build engineer working 20 hours per week.
As shown in the table, 36 different configurations have been run using Spack
(up to 4 versions on each of 10 architecture-compiler-MPI combinations).
Prior to using Spack, only Linux/Intel configurations were automated. The ARES 
team listed a number of key features that enabled the increased automation:
\begin{enumerate}
\item Spack's version tracking and optional dependencies were required to
      build the four configurations with correct libraries;
\item The spec syntax allowed build scripts to test compiler,
      compiler version, and dependency versions concisely---a necessity
      for handling the different architectures;
\item Patching packages for particular platforms was
      necessary to build many packages; and
\item Using a DSL embedded in Python was a significant benefit;
      certain packages required custom scripting to patch.
\end{enumerate}
